---
title: '3.1'
author: "Manish Shah"
date: "2023-04-22"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## 1. Create a barplot of cyl variable of mtcars data with and without using factor argument

Without factor argument

```{r}
data(mtcars)
barplot(table(mtcars$cyl), xlab="Cars CYL", ylab="Frequency", main="Barplot of CYL without factor")
```

With factor argument

```{r}
plot(as.factor(mtcars$cyl), xlab="Cars CYL", ylab="Frequency", main="Barplot(plot) of CYL with factor")
```

## 2. Locate median of mpg variable of mtcars data graphically and compare the median value with in-built function of R

```{r}
hist(mtcars$mpg, main="Histogram of MPG with median")
abline(v=median(mtcars$mpg), lwd=3, lty=2, col="red")
legend("topright", legend="Median", col="red", lwd=3)
axis(side = 1, at = seq(min(mtcars$mpg), max(mtcars$mpg), by = 1), tck = -0.01, labels = FALSE)
```

Median value of mpg from in-built function of R
```{r}
median(mtcars$mpg)
```

***We can the same value from graph & from median function i.e. 19.2***


## 3. Locate mode of mpg variable of mtcars data graphically and compare the mode value with the in-built/custom function of R

```{r}
mode <- 3*median(mtcars$mpg) - 2*mean(mtcars$mpg)
mode

hist(mtcars$mpg, main="Histogram of MPG with mode")
abline(v=mode, lwd=3, lty=2, col="green")
axis(side = 1, at = seq(min(mtcars$mpg), max(mtcars$mpg), by = 1), tck = -0.01, labels = FALSE)
legend("topright", legend = "Mode", fill= "green")
```

From graph, we can notice mode falls in approx 17.5 and we have the calculated mode = 17.41875 

## 4. Create a scatterplot of mgp (dependent) and wt (independent) variable of mtcars data, add ablines at mean plus-minus 2 standard deviation and show the name of the cars with mpg > 2 standard deviation from mean inside the scatterplot obtained above


```{r}
plot(mtcars$wt, mtcars$mpg, ylim=c(0,40), main = "Scatterplot of MPG and Weight", xlab = "Weight", ylab = "Miles per Gallon")

upper_lim <- mean(mtcars$mpg)+2*sd(mtcars$mpg)
lower_lim <- mean(mtcars$mpg)-2*sd(mtcars$mpg)

abline(h=upper_lim, lwd=2, lty=2, col="red")
abline(h=lower_lim, lwd=2, lty=2, col="red")

cat("Search cars with greater than upper_limit value & then use rownames() to get name of cars which will plot in the graph")
text(mtcars$wt[mtcars$mpg > upper_lim], mtcars$mpg[mtcars$mpg > upper_lim], rownames(mtcars)[mtcars$mpg > upper_lim], cex = 0.6, pos=4, col="blue")
```



## 5. Create a x variable with 100 random numbers and y variable with x + 100 random numbers; create a factor variable with 100 monthly random observations, create a time series data with 100 random values starting from January 1970; create a date variable with 100 random values starting from 1970/01/01 increasing each day; create a new variable z with square of x variable

```{r}
set.seed(16)
```

Variable with 100 random numbers
```{r}
set.seed(16)
x <- sample(100, replace = TRUE)
```

Variable with x + 100 random numbers
```{r}
set.seed(16)
y <- x + sample(100, replace = TRUE)
```

Factor variable with 100 random month observation
```{r}
set.seed(16)
month <- factor(sample(month.name, 100, replace = TRUE))
```

Time series data starting from 1970 January
```{r}
set.seed(16)
ts_data <- ts(sample(1:100, 100, replace = TRUE), start = c(1970, 1), frequency = 12)
```


Date variable with 100 random values starting from 1970/01/01

```{r}
set.seed(16)
ts_date <- as.Date("1970/01/01") + sample(0:365, 100, replace = TRUE)
```

Square of x variable
```{r}
z <- x^2
```

Print all the variable created
```{r}
x
y
month
ts_data
ts_date
z
```

## 6. Create a 2 x 3 plot window with scatterplot, barplot, boxplot, time series plot, date plot and square function plot

2x3 plot window
```{r}
par(mfrow=c(2,3))
cat('Scatter plot of x and y')
plot(x, y, main = "Scatterplot of x and y", xlab = "x", ylab = "y")
cat('Bar plot of factor variable month')
barplot(table(month), main = "Barplot of month", xlab = "Month", ylab = "Frequency")
cat('Box plot of ts_data')
boxplot(ts_data, main = "Boxplot of ts_data")

cat('Time series plot of ts_data')
plot(ts_data, main = "Time series plot of ts_data", xlab = "Year", ylab = "Value")

cat('Date plot of ts_date and y')
plot(ts_date, y, main = "Date plot of ts_date and y", xlab = "Date", ylab = "y")

cat('Plot of z vs x')
plot(x, z, main = "Plot of z vs x", xlab = "x", ylab = "z")
par(mfrow=c(1,1))

```

## 7. Perform log transformation on x and z variables i.e. log of x, log of z and log of x and z in the plot command and interpret the results carefully 

Reset window to 1x1 & then plot log(x) & log(y)
```{r fig.show='hold', fig.width=8}
par(mfrow = c(1,3))
plot(x, z, log="x", main = "Plot of log x", xlab = "log(x)", ylab = "z")
plot(x, z, log="y", main = "Plot of log z", xlab = "x", ylab = "log(z)")
plot(x, z, log="xy", main = "Plot of log x and log z", xlab = "log(x)", ylab = "log(z)")
par(mfrow = c(1,1))
```

It shows that there is linear relation when both x & z is log transformed. But when we do log transform separately, the distribution is not uniform & is heavily skewed.


## 8. Create a 1x1 plot window with correlation matrix plot of first three numerical variable of mtcars data (cyl is not numeric, its factor!)


Remove cyl variable 

```{r}
library(dplyr)
mtcars_sub <- select(mtcars, -c(cyl))
```

Get first three numerical variables
```{r}
mtcars_sub <- mtcars_sub[, 1:3]
```

Create a correlation matrix
```{r}
cars_corr <- cor(mtcars_sub)
```

Plot correlation matrix

```{r}
library(corrplot)
corrplot(cars_corr, method = "circle")
```
## 9. Interpret the result of the correlation matrix plot obtained above with respect to the correlation coefficient to be used for each pair

From the correlation plot, we can observe that dark blue has highest correlation & dark red has lowest correlation.

## 10. Write advantage and limitations of plots created using R base packages based on these nine steps

Advantages - 
   - The R base plot is already available without loading any package so we can use it easily.
   - The plots are customizable i.e. we can add lable, topics, ablines, etc.
   - It supports multiple types of graph such as boxplot, barplot, timeseries plot, scatter plot, etc.
   
Limitations - 
   - It takes time to plot for variables containing large numbers of rows
   - It doesn't supports complex graph which can be generated using ggplot2
