---
title: "Assignment 3.2"
author: "Manish Shah"
date: "2023-05-08"
output: html_document
---
```{r message=FALSE}
library(tidyverse)
library(igraph)
```

## 1. Load the attached "termDocMatrix.rdata" file in R/R studio
```{r}
load("D:\\R programming runs\\Assisgnments\\Assignment 3\\Manish Shah - termDocMatrix.rdata")
```

## 2. Check the structure of this data and comment on it carefully
```{r}
str(termDocMatrix)
```
It is a term document matrix with Terms as rows & Values(Docs) as columns where 0,1 & 2 values are stored

## 3. Inspect the first 10 rows and first 10 columns of this data using sub-setting
```{r}
termDocMatrix[1:10, 1:10]
```

## 4. Convert the loaded termDocMatrix data to as matrix with appropriate R code
```{r}
term_matrix <- as.matrix(termDocMatrix)
```

## 5. Change this matrix to a Boolean matrix with same name (Hint: [termDocMatrix >=1] < 1)
```{r}
term_matrix[term_matrix >= 1] <- 1
```

## 6. Transform this matrix to a term-term adjacency matrix as termMatrix object (Hint: Use %*% and ## t(termDocMatrix)
```{r}
term_adj_matrix <- term_matrix %*% t(term_matrix)
```

## 7. Inspect the first 10 rows and first 10 columns of this matrix using sub-setting
```{r}
term_adj_matrix[1:10, 1:10]
```

## 8. Define a graph object g of termMatrix using graph.adjacency function of "igraph" package with weighted=T ## and mode="undirected" arguments in the function
```{r}
g <- graph.adjacency(term_adj_matrix, mode = "undirected", weighted = T)
```

## 9. Remove loops of g using simplify function
```{r}
g <- simplify(g, remove.multiple = TRUE, remove.loops = TRUE)
```

## 10. Set vertices labels with names of g
```{r}
V(g)$label <- V(g)$name
```

## 11. Set degree with degree of g
```{r}
V(g)$degree <- degree(g)
```

## 12. Find degree of g for 'all", "in" and "out" modes and interpret them carefully
```{r}
degree_all <- degree(g, mode = "all")
degree_all

degree(g, mode = "in")
degree(g, mode = "out")
```
Degree means the arrow in & out from a node.
From all degree we can observe that all terms has degree > 5 where the minimum degree is of **applications** i.e. 6 and maximum degree is of **mining** i.e. 20.  
Similarly, degree-in means the number of arrows pointing towards it whereas degree-out means the number of arrows pointing from it.  
The degree is same for all modes because it is ***undirected.***

## 13. Find diameter of g and interpret it carefully
```{r}
diameter(g)
```
The diameter means the longest shortest path between any two nodes. So, in this graph we have diameter of 5.


## 14. Find edge density of g and interpret it carefully
```{r}
edge_density(g)
```
Edge density means the numbers of edges connected to nodes in graph from a node. Here 0.6190476 or 61.90% of nodes have edge connected to other nodes.

## 15. Find reciprocity of g and interpret it carefully
```{r}
reciprocity(g)
```
Reciprocity 1 means all edges in network are reciprocated.
Reciprocated means if two node is connected to each other. Since the graph is undirected so all node are connected to each other, hence reciprocity is 1.

## 16. Find closeness of g and interpret it carefully
```{r}
closeness(g)
```
Closeness means average length of edge from a node to all other nodes. From above, we can observe closeness of all terms is less than 0.01.

## 17. Find betweenness of g and interpret it carefully
```{r}
betweenness(g)
```
Betweenness means how many times a node lies between shortest path of two nodes.

## 18. Plot histogram of node degree and interpret it carefully
```{r}
hist(degree_all, main = "Node Degree Histogram", xlab = "Node Degree")
```

The node degree ranges from 6 to 20 where 6-8 & 10-12 has high degree to vertex & 18-20 is lowest i.e. 1 vertex.

## 19. Set seed as per your class roll number
```{r}
set.seed(16)
```

## 20. plot g with vertex.size of degree*0.4 and interpret it carefully
```{r}
plot(g, vertex.size = degree_all*0.4, main="Twitter Network Graph")
```

From the graph, we can observe that highest degree nodes are in center i.e. ***mining, data, tutorial, analysis, etc*** have high degree.

## 21. plot g with fruchterman.reingold layout and interpret it carefully
```{r}
plot(g, layout=layout.fruchterman.reingold, main="Graph with Fruchterman Reingold Layout")
```

In this graph also we can observe nodes with high degree are in center & lowest are outside.

## 22. plot g with kamada.kawai layout and interpret it carefully
```{r}
plot(g, layout=layout.kamada.kawai)
```

## 23. plot hub and authority of g and interpret them carefully
```{r}
par(mfrow=c(1,2))
hub <- hub_score(g)
authority <- authority.score(g)

plot(hub$vector)
plot(authority$vector)
par(mfrow=c(1,1))

```
Hubs are the outgoing edges & authorities are the incoming egdes. Since the graph is undirected, so the plot is same.

## 24. Plot community cluster of g and interpret it carefully
Detect communities & then plot
```{r}
fc <- cluster_fast_greedy(g)
plot(fc, g, vertex.color = fc$membership, main = 'Community Detection')
```

Here, we  can observe there are 3 communities where ***mining, data*** are overlapped i.e. they belong to two groups.

## 25. Write a summary of SNA for the twitter data
Each nodes are the terms & each edges connected to nodes means the terms are occurred frequently simultaneously. The most used terms in given termdocumentmatrix is ***data*** & ***mining***.
