---
title: "P01"
author: "Manish Shah"
date: "2023-04-21"
output: pdf_document
geometry: "top=2cm"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

```{r}
library(pdftools)
library(tm)
library(wordcloud)
library(graph)
library(Rgraphviz)
library(igraph)
library(topicmodels)
```

***Setting working directory to MDS503P01***

```{r}
knitr::opts_knit$set(root.dir = "D:/R programming runs/Assisgnments/Project 1/MDS503P01")
```

## Getting all the pdf files using regex from working directory

```{r}
pdf_files <- list.files(pattern = "pdf$")
```

## Creating corpus with help of **tm** package

```{r}
pdf_corp <- Corpus(URISource(pdf_files), readerControl=list(reader = readPDF()))
```

## Removing punctuation, stopwords, & converting words to lowercase and then creating ***term document matrix***

```{r}
pdf_tdm <- TermDocumentMatrix(pdf_corp, control = list(removePunctuation=T, 
                                                       stopwords=T, 
                                                       tolower=T, 
                                                       removeNumbers=T))
inspect(pdf_tdm)
```

## Getting most frequent used words where the words will be repeated atleast 25 times

```{r}
pdf.freq <- findFreqTerms(pdf_tdm, lowfreq=25, highfreq=Inf)
pdf.freq
```

\newpage

## Plot word cloud without any colors

We convert term-document matrix(sparse matrix) to regular matrix and then with help of ***wordcloud*** package, we create word cloud

```{r}
m <- as.matrix(pdf_tdm)
freq <- sort(rowSums(m), decreasing=T)
wordcloud(words=names(freq), freq=freq, min.freq=4, random.order=F)
```

\newpage

## Plot word cloud with color

```{r}
my_colors <- sample(colors(), 10)
wordcloud(words=names(freq), freq=freq, min.freq=4, random.order=F, colors = my_colors)

```

\newpage

## Plot network graph from term-document matrix

```{r}
plot(pdf_tdm, terms=pdf.freq, corThreshold=0.8, weighting=T)
```

## Generating topic modeling using topicmodel package

```{r}
set.seed(16)
myLda <- LDA(as.DocumentTermMatrix(pdf_tdm), k=5)
terms(myLda, 10)
```

Here, k=5 denotes 5 topic & 10 in terms() denotes 10 terms in each of the 5 topics  
We can observe that the 'social', 'media', 'marketing', 'online', 'network', etc. are most used terms in all of the topics.
